Reassessing the Impact of Dynamic Slicing in SFL

### 2019-01-25 paper/ijcai/paper.tex
text + todos

\begin{abstract}
  ...
\end{abstract}

@@

\ds{} and \sfl{} are complementary. Intuitively, \ds{} identifies
irrelevant parts of the code whereas \sfl{} ranks the relevant parts
of the code.  This paper reports the results of a comprehensive study
to evaluate the impact of \ds{} to improve \sfl{}. The study involves
\numFaults{} faults from \numPrograms{} programs from the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to
evaluated fault localization research. The intuition for the \comb{}
combination is that several highly ranked statements, albeit covered
by failing executions, may be unrelated to the fault. Prior work
reported promising results in this combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
We found surprising that, despite these findings, no tool or client analyses use this combination
today.\Mar{$\leftarrow$ revise. inconsistent. there is a recent paper
  building on that idea...from 2018.} Several reasons could justify that observation. One hypothesis is that results reported in prior work are
over-optimistic. For example, most prior work evaluated improvements
of \sfl{} techniques using relative metrics, which are based on the
position of the first faulty statements found in the ranking relative
to the total number of ranked statements, which is often a large
number. As such, it inflates actual improvements and deceives
potential adopters of the technology. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
pointed to that fact and encouraged researchers to adopt more precise metrics,
such as \topk{}
\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359},
which has been widely adopted to evaluate performance of information retrieval algorithms~\Fix{cite}. This
metric reports the percentage of faults captured by a technique when
the rank is trimmed to the first $k$ components.

@@

The first question addresses an important problem associated with
dynamic slicing techniques---that of missing faulty
statements. Naturally, the consequence of that problem for debugging
is that developers would never be able to locate faults. Different
slicers can miss faulty statements for different reasons. In this
paper, we used Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310},
which, in principle, could miss statements because of imprecise
oracles that guide the slicing process. We evaluated how often that
important problem happens in our experiments. The second research
questions effectively evaluates the impact of the combination. To sum,
our results show that \Fix{write a paragraph about this...}

The contributions of this work are as follows:
\begin{itemize}
	\item A comprehensive study on the combination of \sfl{} and \ds{}
     for bug localization of \emph{Java} faulty programs.
	%\item Empirical evidence that the \comb{} combination improves 
\end{itemize}

@@

\Sof{@TODO: Melhorar terminologia e algoritmo} Critical Slicing takes as input a function of interest that can be designed according to the problem to be solved. The function of interest (Algorithm \ref{alg:finc}) determines if the test case output is interesting or not. In this study, interesting means that the test execution path is equal to the expected one. This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception. The authors assume that it is only necessary to compare both stack traces until the call where the test fails. For each chunk under evaluation, the test is executed without considering the chunk under evaluation (Algorithm \ref{alg:finc}, line 2). Both test ($testStk$) and expected ($expStk$) stack traces are filtered according to the position of the test call fails. These operations are performed by line 3 and 4 from Algorithm 2. Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.

@@

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      \toprule
      Project            & Size (kLOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
      \midrule
      \lang{}            & 111751  & 6057 & 65       \\   %\commentst{& 124   &  -}\\
      \cmath{}           & 306276  & 26797 & 106     \\   %\comments{& 177   &  -}\\
      \closure{}         & 149521  & 27930  & 133     \\   %\comments{& 350   &  -}\\
      \chart{}           & 230159  & 8458 & 26      \\  %\comments{& 92    &  -}\\
      \jtime{}           & 141610  & 3289 & 27       \\   %\comments{& 76    &  -}\\
      \mockito{}         & 22787  & 8835 & 38    \\     %\comments{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.\Mar{numbers seem too
    big. is this really in
    *k*LOC or just LOC? please, confirm.}}
\label{tab:df4j}
\end{table}
\normalsize

@@

The evaluation techniques are SFL and \comb{}-$k$, for
$k\in\{5,10\}$. \Mar{Simplified and moved this par. from Section
  4.0. I noticed you used this terminology (\comb{} with ``-k'')
  below. Please, explain and provide rationale}.

To be able to effectively compare \comb{}-k against SFL, we first reduce the SFL report to method components. This reduction is done by considering the highest fault probability of the top-k components of each fault (/subject), to effectively be able to compare method-level diagnostic effort between the
two approaches. A variety in diagnostic effort is measured
using\Mar{$\leftarrow$Sofia, I found this par. confusing.}

@@

where C is the cost of diagnosis. \Sof{Need to explain this better}
A positive $\Delta$C means that the faulty component has risen in
the ranking reported by SFL techniques when DS is used,
yielding a lowered cost of diagnosing.

@@

Table \ref{tab:red} reports the reduction of statements after using \ds{} to minimize the top-5 and top-10 of classes of the subjects. The reduction percentage decreases 5.66\% if the top-10 is considered instead of the top-5.

@@

In \textbf{RQ1}, we evaluate how often DS misses faulty statements, since it is one of the main problems of dynamic slicing techniques.

Table \ref{table:fsws} presents the number of faults (/subjects) whose the faulty statement(s) are in the top-5 and top-10 of the highest ranked classses only using \sfl{}, i.e., not applying \ds{}. The gain from considering the top-10 of classes instead of top-5 is small or null.

@@

		            & \% top-5 & \% top-10  & $\Delta$ & \# top-5 & \% top-5 & \# top-10 & \% top-10 &  \\ 
		\midrule
		% \lang{}            & 84.60 \% & 84.60 \% & 0 \%       \\   %\commentst{& 124   &  -}\\
		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.6\% & 26    \\  %\comments{& 92    &  -}\\
		\jtime{}           & 77.8 \%  & 100.0 \% & 22.2 \%  & 22 & 81.5\% & 23 & 85.2\% & 27     \\   %\comments{& 76    &  -}\\
		 \mockito{}         & 63.2\%  & 71.1\% & 7.9\%   & 27 & 71.1\% & 30 & 79.0\% & 38 \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Number of versions where at least one of the buggy-lines is in the SFL and SFL+DS-$k$ report}
  \label{table:fsws}
\end{table*}

@@

\Sof{@todo: Answer the question}

@@

The \comb{} combination yields an average improvement of, approximately, 19\% on the ranking of the faulty statements of the \chart{}
project. Figure \ref{table:performance}, reports the average rank of all faulty statements for each version of \chart{} project after
applying the 3 techiniques \sfl{}, \comb{}-5 and \comb{}-10.

Table \ref{tab:diagnosis} reports the performance of the diagnosis using \comb{}-5 and \comb{}-10 instead of only using \sfl{}. $\Delta<0$ means that the faulty statement may be removed. $\Delta=0$ means that the faulty statement remained in the same position. $\Delta>0$ means that \ds{} improved diagnosability. For both \comb{}-5 and \comb{}-10, diagnosability increases 55.56\%. However, top-5 has less classes to minimize than top-10.

@@

			\bottomrule
		\end{tabular}
		\caption {\chart{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
		\label{tab:diagnosis}
	\end{table}
	\normalsize

@@

			\bottomrule
		\end{tabular}
		\caption {\jtime{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
		\label{tab:diagnosis}
	\end{table}
	\normalsize

@@

			\bottomrule
		\end{tabular}
		\caption {\mockito{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
		\label{tab:diagnosis}
	\end{table}
	\normalsize

>>>>

\begin{abstract}
  \Sof{@todo}
\end{abstract}

@@

\ds{} and \sfl{} are complementary. Intuitively, \ds{} identifies
irrelevant parts of the code whereas \sfl{} ranks the relevant parts
of the code.  This paper reports the results of a comprehensive study
to evaluate the impact of \ds{} to improve \sfl{}. The study involves
\numFaults{} faults from \numPrograms{} programs from the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to
evaluated fault localization research. The intuition for the \comb{}
combination is that several highly ranked statements, albeit covered
by failing executions, may be unrelated to the fault. Prior work
reported promising results in this combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
We found surprising that, despite these findings, no tool or client analyses use this combination
today.\Sof{@todo: Revise this and look to the paper from 2018} Several reasons could justify that observation. One hypothesis is that results reported in prior work are
over-optimistic. For example, most prior work evaluated improvements
of \sfl{} techniques using relative metrics, which are based on the
position of the first faulty statements found in the ranking relative
to the total number of ranked statements, which is often a large
number. As such, it inflates actual improvements and deceives
potential adopters of the technology. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
pointed to that fact and encouraged researchers to adopt more precise metrics,
such as \topk{}
\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359},
which has been widely adopted to evaluate performance of information retrieval algorithms~\Fix{cite}. This
metric reports the percentage of faults captured by a technique when
the rank is trimmed to the first $k$ components.

@@

The first question addresses an important problem associated with
dynamic slicing techniques---that of missing faulty
statements. Naturally, the consequence of that problem for debugging
is that developers would never be able to locate faults. Different
slicers can miss faulty statements for different reasons. In this
paper, we used Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310},
which, in principle, could miss statements because of imprecise
oracles that guide the slicing process. We evaluated how often that
important problem happens in our experiments. The second research
questions effectively evaluates the impact of the combination. To sum,
our results show that \Sof{@todo: sum up the results}.

The contributions of this work are as follows \Sof{Finish this}:
\begin{itemize}
	\item A comprehensive study on the combination of \sfl{} and \ds{}
     for bug localization of \emph{Java} faulty programs.
	%\item Empirical evidence that the \comb{} combination improves 
\end{itemize}

@@

\Sof{@todo: Definatelly not near of finished, revise it and possibly redo it} Critical Slicing takes as input a function of interest that can be designed according to the problem to be solved. The function of interest (Algorithm \ref{alg:finc}) determines if the test case output is interesting or not. In this study, interesting means that the test execution path is equal to the expected one. This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception. The authors assume that it is only necessary to compare both stack traces until the call where the test fails. For each chunk under evaluation, the test is executed without considering the chunk under evaluation (Algorithm \ref{alg:finc}, line 2). Both test ($testStk$) and expected ($expStk$) stack traces are filtered according to the position of the test call fails. These operations are performed by line 3 and 4 from Algorithm 2. Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.

@@

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      \toprule
      Project            & Size (kLOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
      \midrule
      \lang{}            & 111751  & 6057 & 65       \\   %\commentst{& 124   &  -}\\
      \cmath{}           & 306276  & 26797 & 106     \\   %\comments{& 177   &  -}\\
      \closure{}         & 149521  & 27930  & 133     \\   %\comments{& 350   &  -}\\
      \chart{}           & 230159  & 8458 & 26      \\  %\comments{& 92    &  -}\\
      \jtime{}           & 141610  & 3289 & 27       \\   %\comments{& 76    &  -}\\
      \mockito{}         & 22787  & 8835 & 38    \\     %\comments{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.\Mar{numbers seem too
    big. is this really in
    *k*LOC or just LOC? please, confirm.}\Sof{I think it is a mistake and the unit should be LOC. But I will check.}}
\label{tab:df4j}
\end{table}
\normalsize

\Sof{@todo: Add pie chart to show the distribution of foos}

@@

The evaluation techniques are SFL and \comb{}-$k$, for
$k\in\{5,10\}$. \Mar{Simplified and moved this par. from Section
  4.0. I noticed you used this terminology (\comb{} with ``-k'')
  below. Please, explain and provide rationale}.\Sof{Not sure if it is the right one, an alterantive is using only SFL+DS
  and instead of top-5 and top-10 use K = 5 and K = 10... Which do you think is the best?}

To be able to effectively compare \comb{}-k against SFL, we first reduce the SFL report to method components. This reduction is done by considering the highest fault probability of the top-k components of each fault (/subject), to effectively be able to compare method-level diagnostic effort between the
two approaches. A variety in diagnostic effort is measured
using\Sof{@todo: revise it, it is confusing}

@@

where C is the cost of diagnosis. \Sof{@todo: Need to explain this better}
A positive $\Delta$C means that the faulty component has risen in
the ranking reported by SFL techniques when DS is used,
yielding a lowered cost of diagnosing.

@@

Table \ref{tab:red} reports the reduction of statements after using \ds{} to minimize the top-5 and top-10 of classes of the subjects.

@@

In \textbf{RQ1}, we evaluate how often \ds{} misses faulty statements, since it is one of the main problems of dynamic slicing techniques.

Table \ref{table:fsws} presents the number of faults where at least one of the faulty statements appears in the final reports of both techniques, \sfl{} and \comb{}-k.

@@

		            & \% top-5 & \% top-10  & $\Delta$ & \# top-5 & \% top-5 & \# top-10 & \% top-10 &  \\ 
		\midrule
		% \lang{}            & 84.60 \% & 84.60 \% & 0 \%       \\   %\commentst{& 124   &  -}\\
		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.6\% & 26    \\  %\comments{& 92    &  -}\\
		\jtime{}           & 77.8 \%  & 100.0 \% & 22.2 \%  & 22 & 81.5\% & 23 & 85.2\% & 27     \\   %\comments{& 76    &  -}\\
		 \mockito{}         & 63.2\%  & 71.1\% & 7.9\%   & 27 & 71.1\% & 30 & 79.0\% & 38 \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the buggy-lines is in the SFL and SFL+DS-$k$ report \Sof{@todo: Add absolute numbers for SFL}}
  \label{table:fsws}
\end{table*}

@@

@@

The \comb{} combination yields an average improvement of, approximately, 19\% on the ranking of the faulty statements of the \chart{}
project. Table \ref{table:performance}, reports the average rank of all faulty statements for each version of \chart{} project after
applying the 3 techiniques \sfl{}, \comb{}-5 and \comb{}-10.

Table \ref{tab:diagnosis} reports the performance of the diagnosis using \comb{}-5 and \comb{}-10 instead of only using \sfl{}. $\Delta C <0$ means that the faulty statement may be removed. $\Delta C=0$ means that the faulty statement remained in the same position. $\Delta C >0$ means that \ds{} improved diagnosability.

%For both \comb{}-5 and \comb{}-10, diagnosability increases 55.56\%. However, top-5 has less classes to minimize than top-10.

@@

			\bottomrule
		\end{tabular}
		\caption {\chart{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
		\label{tab:diagchart}
	\end{table}
	\normalsize

@@

			\bottomrule
		\end{tabular}
		\caption {\jtime{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
		\label{tab:diagtime}
	\end{table}
	\normalsize

@@

			\bottomrule
		\end{tabular}
		\caption {\mockito{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
		\label{tab:diagmockito}
	\end{table}
	\normalsize
